\begin{thebibliography}{10}
\bibitem{secTest}{GUPTA, Kamlesh and Sanjay SILAKARI. ECC over RSA for Asymmetric Encryption: A Review. International Journal of Computer Science Issues. 2011, 8(05). Also available at: \url{https://pdfs.semanticscholar.org/45ef/c85c2a92fe00dae5477f918795d9fd23e6e5.pdf}.}

\bibitem{algGeom} {COX, David A., John LITTLE and Donal O'SHEA. \textit{Ideals, Varieties, and Algorithms: An Introduction to Computational Algebraic Geometry and Commutative Algebra.} Fourth Edition. New York: Springer, 2015. Undergraduate texts in mathematics. ISBN 978-3-319-16721-3.}

\bibitem{mky} {KALVODA, Tomáš, Ivo PETR and Štěpán STAROSTA. Matematika pro kryptologii [online]. KAM FIT ČVUT. [Praha], Updated on 20-02-2019 [Accessed on 16-04-2019]. Available at: \url{https://courses.fit.cvut.cz/MI-MKY/media/lectures/mi-mky-poznamky-v17.pdf}}

\bibitem{myBP} {HOLLMANN, Matyáš. \textit{Implementace násobení na neasociativních (nekomutativních) algebrách.} Praha, 2017. Bakalářská práce. České vysoké učení technické v Praze, Fakulta informačních technologií. Vedoucí práce Jiřina Scholtzová. Also available at: \url{https://dspace.cvut.cz/bitstream/handle/10467/69263/F8-BP-2017-Hollmann-Matyas-thesis.pdf}}

\bibitem{bruno}{BUCHBERGER, Bruno. Bruno Buchberger's PhD thesis 1965: An Algorithm for Finding the Basis Elements of the Residue Class Ring of a Zero Dimensional Polynomial Ideal. Journal of Symbolic Computation. 2006, 41(03), 475-511. DOI: \url{https://doi.org/10.1016/j.jsc.2005.09.007}}

\bibitem{week11}{BROWN, Gavin. \textit{Zero-dimensional ideals}. Chapter 9 in Polynomials in Several Variables - MA574 (course notes) [online]. 2016. [Accessed on 16-04-2019]. Available at: \url{https://www.kent.ac.uk/smsas/personal/gdb/MA574/week11.pdf}.}

\bibitem{handbook}{COHEN, Henri, Gerhard FREY and Roberto AVANZI. \textit{Handbook of elliptic and hyperelliptic curve cryptography.} Boca Raton: Taylor \& Francis, 2006. ISBN 978-1-58488-518-4.}

\bibitem{shoup}{SHOUP, Victor. \textit{Lower Bounds for Discrete Logarithms and Related Problems.} Advances in Cryptology — EUROCRYPT ’97. EUROCRYPT 1997. Springer, Berlin, Heidelberg, 1997. DOI: \url{https://doi.org/10.1007/3-540-69053-0_18}.}

\bibitem{polProb}{BOS, Joppe W., Alina DUDEANU and Dimitar JETCHEV. \textit{Collision bounds for the additive Pollard rho algorithm for solving discrete logarithms.} Journal of Mathematical Cryptology. 2014, 8(1), 71-92. ISSN (Online) 1862-2984. DOI: \url{https://doi.org/10.1515/jmc-2012-0032}.}

\bibitem{PH}{POHLIG, S. and M. HELLMAN. \textit{An improved algorithm for computing logarithms over $GF(p)$ and its cryptographic significance (Corresp.)}. IEEE Transactions on Information Theory. 1978, 24(1), 106-110.  ISSN (Online) 1557-9654 DOI: \url{https://doi.org/10.1109/TIT.1978.1055817}.}

\bibitem{subExp}{GALBRAITH, Steven D. \textit{Mathematics of public key cryptography.} New York: Cambridge University Press, 2012. ISBN 978-1-107-01392-6.}

\bibitem{amadori17}{AMADORI, Alessandro, Federico PINTORE and Massimiliano SALA. \textit{On the discrete logarithm problem for prime-field elliptic curves}. Finite fields and their applications. 2018, 51(May), 168-182. DOI: \url{https://doi.org/10.1016/j.ffa.2018.01.009}.}

\bibitem{semaev04}{SEMAEV, Igor. \textit{Summation polynomials and the discrete logarithm problem on elliptic curves.} Cryptology ePrint Archive, Report 2004/031, 2004. Also available at: \url{https://eprint.iacr.org/2004/031}.}

\bibitem{semaev15}{SEMAEV, Igor. \textit{New algorithm for the discrete logarithm problem on elliptic curves.} Cryptology ePrint Archive, Report 2015/310, 2015. Also available at \url{https://eprint.iacr.org/2015/310}.}

\bibitem{FGLM}{FAUGÉRE, J.C., P. GIANNI, D. LAZARD and T. MORA. \textit{Efficient Computation of Zero-dimensional Gröbner Bases by Change of Ordering}. Journal of Symbolic Computation. 1994, 11(1-000). Also available at: \url{https://www-polsys.lip6.fr/~jcf/Papers/FGLM.pdf}.}

\bibitem{grobComp}{CAMINATA, Alessio and Elisa GORLA. \textit{Solving Multivariate Polynomial Systems and an Invariant from Commutative Algebra.} Cryptology ePrint Archive, Report 2017/593, 2017. Also available at: \url{https://eprint.iacr.org/2017/593}.}

\bibitem{macal}{JÓNSSON, Gudbjörn F. and Stephen A. VAVASIS. \textit{Accurate solution of polynomial equations using Macaulay resultant matrices}. Mathematics of Computation. 2004, 74(249), 221-262. Also available at:
\url{http://www.ams.org/journals/mcom/2005-74-249/S0025-5718-04-01722-3/S0025-5718-04-01722-3.pdf}.}

\bibitem{guire}{McGUIRE, Gary and Daniela MUELLER. \textit{A New  Index Calculus Algorithm for the Elliptic Curve Discrete Logarithm Problem and Summation Polynomial Evaluation.} Cryptology ePrint Archive, Report 2017/1262, 2017. Also available at: \url{https://eprint.iacr.org/2017/1262}.}

\bibitem{magma}{BOSMA, Wieb, John CANNON and Catherine PLAYOUST, \textit{Magma Computational Algebra System.} [online] Copyright © 2010-2019. Accessed on [01-05-2019]. Available at: \url{http://magma.maths.usyd.edu.au/magma/}.}

\bibitem{gbComp}{PEARCE, Roman. \textit{Roman Pearce: Groebner Bases}. [online] 2016. Accessed on [01-05-2019].
Available at: \url{http://www.cecm.sfu.ca/~rpearcea/mgb.html}.}

\bibitem{sage}{STEIN, W. A. et al., \textit{SageMath Mathematical Software System - Sage (Version 8.7 (2019-03-23)).}
The Sage Development Team, 2019 [online]. Accessed on [01-05-2019]. Available at: \url{http://www.sagemath.org/}.}

\bibitem{brick}{BRICKENSTEIN, Michael. \textit{Slimgb: Gröbner bases with slim polynomials.} Revista Matemática Complutense. 2010, 23(2), 453-466. ISSN 1139-1138. DOI: \url{http://link.springer.com/10.1007/s13163-009-0020-0}.}

\bibitem{fgb}{FAUG\`{E}RE, J.-C., \textit{FGb: A Library for Computing Gröbner Bases. Version 1.68 (build 14539). [online]} Updated on 31.07.2015. Accessed on [10-04-2019]. Available at: \url{https://www-polsys.lip6.fr/~jcf/FGb/index.html}.}

\bibitem{giac}{PARISSE, Bernard and Renée De GRAEVE, \textit{Giac/Xcas (Version 1.5.0-3)} [online]. Updated in September 2018. Accessed on [15-04-2019]. Available at: \url{https://www-fourier.ujf-grenoble.fr/~parisse/giac.html}.}

\end{thebibliography}